Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-26 paper/paper.tex
started future work section

\section*{Conclusion}
\section*{Future Work}

>>>>

\section*{Conclusion}
\section*{Future Work}
The results achieved over this dataset were significant. In order to show that
the techniques are general, though, we would like to run the same experiments on
other datasets, with different types of items and user behavior. Most of the 
assumptions made for this model were not specific to the data used, and so we 
hope to achieve similar results. It would also be interesting to see how 
different the learned parameters would be for other datasets and how well 
the techniques could perform using the same parameters learned here.

We would also like to investigate the use of latent variable
